\emph{icepack}: a new glacier flow modeling package in Python, version 1.0

### 2021-04-06 reviews/response-1.tex

\item[L100] \textcolor{blue}{Not clear where the Legendre transform enters: the viscous and frictional
dissipation can be read off from Eq. 4.}

Other reviewers didn't find this digression useful so we've removed it.

\item[Eqs. 6 and 12]\textcolor{blue}{While I understand that it is convenient to manipulate the
action to reflect the algebraic manipulations to yield the analytical SIA
solution, the break in symmetry between Eq. 6 and Eq. 12 is frustrating,
given that they both are name `gravity', and that they should in some
sense be the same regardless of which strain rates are assumed to be zero.}

These modules were implemented by two different authors, the SSA / hybrid models by myself (DRS) and the SIA model by Jessica Badgeley (second author) as a project for her PhD thesis and to learn more about finite element analysis.
We recognize that there's a discrepancy here and this will be corrected in future releases of the package.

### 2021-04-06 icepack.tex
Correct names
Truly brutal correction

\Author[1]{Daniel}{Shapero}
\Author[2]{Jessica}{Badgeley}
\Author[2]{Andrew}{Hoffmann}
\Author[1]{Ian}{Joughin}

@@

The evolution equations determining for ice thickness and velocity are necessary for any realistic glacier simulation, but other fields with their own evolution equations can be a part of the problem as well.
The rheology and friction are the main coefficients in the diagnostic equation.
These coefficients are functions of other fields that have their own evolution equations.
For example, the rheology is a function of temperature, englacial water content, and damage from crevassing.
Likewise, the friction coefficient can be described in terms of the subglacial water pressure and a roughness factor for the underlying bedrock \citep{cuffey2010physics}.
The diagnostic and prognostic equations can then be supplemented with evolution equations for these fields, for example the heat equation for temperature, or a hydrology model for subglacial water pressure.

>>>>

\Author[1]{Daniel R}{Shapero}
\Author[2]{Jessica A}{Badgeley}
\Author[2]{Andrew O}{Hoffmann}
\Author[1]{Ian R}{Joughin}

@@

Other fields with their own evolution equations can be a part of the problem as well as thickness and velocity.
The rheology and friction are the main coefficients in the diagnostic equation.
These coefficients are functions of other fields that have their own evolution equations.
For example, the rheology is a function of temperature, englacial water content, and damage from crevassing.
Likewise, the friction coefficient can be described in terms of the subglacial water pressure and a roughness factor for the underlying bedrock \citep{cuffey2010physics}.
The diagnostic and prognostic equations can then be supplemented with evolution equations for these fields, for example the heat equation for temperature, or a hydrology model for subglacial water pressure.
